Spitzer, Gaia and the Potential of the Milky Way

### 2013-08-02 text/paper1/paper.tex
make figure bigger in text
figure captions

\begin{figure}[h]
\begin{center}
\includegraphics[width=0.45\textwidth]{/Users/adrian/projects/streams/plots/paper1/ps_distance.pdf}
\caption{ todo }\label{fig:ps_distance}
\end{center}
\end{figure}

@@

\begin{figure}[h]
\begin{center}
\includegraphics[width=0.45\textwidth]{/Users/adrian/projects/streams/plots/paper1/bootstrap.pdf}
\caption{ todo }\label{fig:bootstrap}
\end{center}
\end{figure}

@@

%With a justified probabilistic framework, we will also be able to provide iven sufficient data, position and motion of the original host could be solved for as additional free parameters, but the effectiveness of this approach has yet to be investigated.

>>>>

\begin{figure}[h]
\begin{center}
\includegraphics[width=0.5\textwidth]{/Users/adrian/projects/streams/plots/paper1/ps_distance.pdf}
\caption{Phase space distance ($D_{\rm ps}$) for 10 stars integrated backwards in the correct potential (top) and a potential where $q_z$ is 25\% larger (bottom). The same 10 particles are used in both figures, so the initial conditions are identical. Red (thick, solid line) shows the galactocentric distance of the progenitor (in arbitrary, normalized units) over the integration. Horizontal (dashed) line shows $D_{\rm ps}=\sqrt{2}$.}\label{fig:ps_distance}
\end{center}
\end{figure}

@@

\begin{figure}[h]
\begin{center}
\includegraphics[width=0.45\textwidth]{/Users/adrian/projects/streams/plots/paper1/bootstrap.pdf}
\caption{ Blue points show the ``best-fit'' parameters resulting from each bootstrap resample of 100 stars from the Sgr stream particle density shown in Figure~\ref{fig:lm10}. Green (vertical and horizontal) lines show the true values of the parameters. Grey ellipses show one- and two-sigma margins, assuming the points are normally distributed. }\label{fig:bootstrap}
\end{center}
\end{figure}

@@

%With a justified probabilistic framework, we will also be able to provide ... given sufficient data, position and motion of the original host could be solved for as additional free parameters, but the effectiveness of this approach has yet to be investigated.
